Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-20 analysis/paper/paper.Rmd
Correct caption that was incomplete

```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a "}
p <-
  ggplot(data = rrpp, aes(x = reproducibility_score)) +
  geom_histogram(binwidth = 10,
                 fill = "black",
                 colour = "black") +
  xlab("Reproducibility score (%)")

>>>>

```{r reproScore, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Reproducibility scores of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialised journals. Where 0 was not reproducible in any fashion and a perfect score would be 100% as evaluated for four areas software citations, software availability, computational methods availability and data availability on a 0 to 3 scale and converted to a percent of total possible score value."}
p <-
  ggplot(data = rrpp, aes(x = reproducibility_score)) +
  geom_histogram(binwidth = 10,
                 fill = "black",
                 colour = "black") +
  xlab("Reproducibility score (%)")
